Attack-Tolerance in Structured Networks via Multipath Routing

### 2016-02-24 ec-2016/source/paper.tex
Add abstract and CCS codes.

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
\\ Draft: 2016-02-21
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

\begin{abstract}
TODO
\end{abstract}

@@

\begin{CCSXML}
<ccs2012>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{TODO~TODO}

@@

Thus, we have shown that assuming the partial trust model, with trust transitive
for $h$ hops, we can construct $2^h$ paths on a wraparound butterfly topology
which do not intersect outside the trusted neighborhoods of the source and
destination.
This is a lower bound on the value $B$ in Equation (\ref{eq:pf),
showing that the decentralized, redundant, structured networks such as the
butterfly can have a very low probability of failure when faced with
adverarial faults, even from a very powerful attacker.

>>>>

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

\begin{abstract}
Networks with single points of failure are particularly susceptible
to adversarial faults,
in which an attacker creates faults strategically at central points.
Centralized network architectures necessarily exhibit this vulnerability,
leading to a growing popularity in decentralized architectures.
However, decentralized architectures do not guarantee the absence of single
points of failure, and networks such as the Internet and World-Wide Web have
been shown theoretically and historically to be highly susceptible to
adversarial faults.
We develop a partial trust model which makes weaker transitivity
assumptions than common web of trust models.
Using this model, we propose a general multipath fault tolerance technique for
structured networks which
provides asymptotic security against adversarial faults.
We also provide a specific algorithm for implementing this technique on the
butterfly network topology.
When network topology can be dictated, these results can be used to create scalable, attack-tolerant infrastructures.
More generally, our results provide a formalism for evaluating the effects
of network structure on adversarial fault tolerance.
\end{abstract}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986</concept_id>
<concept_desc>Security and privacy~Formal methods and theory of security</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003034</concept_id>
<concept_desc>Networks~Network architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010971.10010972.10010540</concept_id>
<concept_desc>Software and its engineering~Peer-to-peer architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Formal methods and theory of security}
\ccsdesc[500]{Networks~Network architectures}
\ccsdesc[500]{Software and its engineering~Peer-to-peer architectures}

@@

Thus, we have shown that assuming the partial trust model, with trust transitive
for $h$ hops, we can construct $2^h$ paths on a wraparound butterfly topology
which do not intersect outside the trusted neighborhoods of the source and
destination.
This is a lower bound on the value $B$ in Equation (\ref{eq:pf}),
showing that the decentralized, redundant, structured networks such as the
butterfly can have a very low probability of failure when faced with
adverarial faults, even from a very powerful attacker.
